Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-03-16 manuscript.tex
more updates to sn section

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN. 
%
Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

>>>>

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Figure~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.  The index behavior of $\gamma$ can be seen by the values displayed in Table~\ref{tab:cp_values} because the $\gamma$ values are ordered by the magnitude of the skewness of $\alpha$ rather than taking into account the direction of the skewness.
%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 0.757	&	 0.427	&	 0.881 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.636 \\
6	&	 0.787	&	 0.381	&	 1.132\\
10	&	 0.794	&	 0.370	&	 1.204\\
\hline
   \end{tabular}
   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Figure~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.  Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.
